Variable Selection

### 2015-07-21 cluster.rmd
transferred Role info to JD.Second

# library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
# library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
# library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
# library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
# library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library('fpc', lib='C:/Progra~1/R/R-3.2.1/library')
# library('vegan', lib = 'C:/Progra~1/R/R-3.2.1/library')
# library(devtools,lib='C:/Progra~1/R/R-3.2.1/library')
# library('ggbiplot',lib='C:/Progra~1/R/R-3.2.1/library')
# library('RcmdrPlugin.BCA',lib='C:/Progra~1/R/R-3.2.1/library')

library('RcmdrPlugin.BCA')
library(devtools)
library('ggbiplot')
library('fpc')
library('vegan')
library('knitr')
library('ggplot2')
library("plyr")
library("dplyr")
library('magrittr')
library('reshape2')
library("rpart")
library('car')
library('e1071')
library('corrgram')
library('party')
library('dendextend')
library('FNN')
library('caret')

# 
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
# opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
# opts_knit$set(root.dir= "C:/Users/n9232371/Documents/Consultbusiness/data")
# all7c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7c.csv')[,-1]
all7c<- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all7c.csv')[,-1]
all7c$Post.Code<- as.factor(all7c$Post.Code)

@@

        }
inv.knn(df= all7d, predict= 'inv.mlsto', new.cases= 2000, k=3)

@@

>>>>

library('knitr', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('ggplot2', lib = 'C:/Progra~1/R/R-3.2.1/library')
library("plyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library("dplyr",lib = 'C:/Progra~1/R/R-3.2.1/library')
library('magrittr',lib='C:/Progra~1/R/R-3.2.1/library')
library('reshape2',lib='C:/Progra~1/R/R-3.2.1/library')
library("rpart",lib = 'C:/Program Files/R/R-3.2.1/library')
library('car', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('e1071', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('corrgram', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('party', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('randomForest', lib = 'C:/Progra~1/R/R-3.2.1/library')
library('fpc', lib='C:/Progra~1/R/R-3.2.1/library')
library('vegan', lib = 'C:/Progra~1/R/R-3.2.1/library')
library(devtools,lib='C:/Progra~1/R/R-3.2.1/library')
library('ggbiplot',lib='C:/Progra~1/R/R-3.2.1/library')
library('RcmdrPlugin.BCA',lib='C:/Progra~1/R/R-3.2.1/library')
library('FNN', lib='C:/Progra~1/R/R-3.2.1/library')
library('caret', lib='C:/Progra~1/R/R-3.2.1/library')

library('RcmdrPlugin.BCA')
# library(devtools)
# library('ggbiplot')
# library('fpc')
# library('vegan')
# library('knitr')
# library('ggplot2')
# library("plyr")
# library("dplyr")
# library('magrittr')
# library('reshape2')
# library("rpart")
# library('car')
# library('e1071')
# library('corrgram')
# library('party')
# library('dendextend')
# library('FNN')
# library('caret')

# 
# setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")
# setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
# opts_knit$set(root.dir= "~/OneDrive/shared files/Bligh Tanner/masters/data")
# opts_knit$set(root.dir= "C:/Users/n9232371/Documents/Consultbusiness/data")
all7c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all7c.csv')[,-1]
# all7c<- read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all7c.csv')[,-1]
all7c$Post.Code<- as.factor(all7c$Post.Code)

@@

}

inv.knn(df= all7d, predict= 'inv.mlsto', new.cases= 2000, k=3)

@@

Retrieve nearest neighbour - categorical
Need to create binary matrix!!

```{r, echo=FALSE}
# want to use the following cat variables for knn:
# Discipline, Business, Biz.type, code.contact, code.client, JD.Second, Billing.Type
# in order to use model.matrix, need to convert NA's to 'unknown' factor.

#trial model.matrix function
vars.vec<- c('Discipline','Business','Biz.type','code.contact', 'code.client', 'JD.Second', 'Billing.Type')

binary.build<- function(vars= vars.vec, df= all7d){
        options("contrasts")
        #create final df bin.knn
        bin.knn= rep(0, nrow(df))
        #loop through each variable in vars vector
        for(i in 1:2){
                temp = data.frame(df[, vars[i]])
                colnames(temp)<- c(vars[i])
                formula = paste('~',vars[i],'-1')
                a= model.matrix( as.formula(formula), temp)
                a= a[match(rownames(temp), rownames(a)),]
                bin.knn= cbind(bin.knn,a)
        }

        print(bin.knn)
}

binary.build(vars= vars.vec, df= all7d) %>% head
```

### 2015-07-21 var_select.rmd
more clust
transferred Role info to JD.Second

```{r load_data, echo=FALSE}
all6a<- read.csv('all6a.csv')[,-1]
all6a$Start.Date<- as.Date(all6a$Start.Date)
all7<- read.csv('all7.csv')[,-1]
all7$Start.Date<- as.Date(all7$Start.Date)
```

@@

# write.csv(all7a,'all7a.csv')
all7a<- read.csv('all7a.csv')
```

@@

#merge client.age column of details to all7b by code.client
all7b<- merge(all7b, details %>% select(code, client.age), by.x = 'code.client', by.y = 'code', all.x=TRUE, all.y=FALSE)
# write.csv(all7b, 'all7c.csv')
all7c<- read.csv('all7c.csv')[,-1]

@@

write.csv(all7c, 'all7c.csv')
all7c<- read.csv('all7c.csv')[,-1]

>>>>

```{r load_data, echo=FALSE}
all7<- read.csv('all7.csv')[,-1]
all7$Start.Date<- as.Date(all7$Start.Date)
```

@@

# write.csv(all7a,'all7a.csv')
all7a<- read.csv('all7a.csv')[,-1]
```

@@

#merge client.age column of details to all7b by code.client
all7b<- merge(all7b, details %>% select(code, client.age), by.x = 'code.client', by.y = 'code', all.x=TRUE, all.y=FALSE)

# write.csv(all7b, 'all7c.csv')
all7c<- read.csv('all7c.csv')[,-1]

@@

# write.csv(all7c, 'all7c.csv')
all7c<- read.csv('all7c.csv')[,-1]
